Flexibility of interactions depends on habitat suitability

### 2019-07-30 paper/manuscript.Rmd
Some more Tylianakis and Peralta 2015

@@

>>>>

In addition to seasonal patterns, interaction turnover can be driven by environmental fac- tors, such as community changes during drought years (Alarco ́n et al. 2008) or along land use or landscape intensity gradients (Gagic et al. 2012, Laliberte ́ & Tylianakis 2010). The impact of environmental conditions on interaction turnover can, in turn, be constrained by species traits such as feeding morphology (Carnicer et al. 2009) or body size (Laliberte ́ & Tylianakis 2010). To understand this balance, species interactions can be thought of as having both a niche-based or trait-based component and a random or neutral component determined by encounter probability (Bartomeus et al. 2016, Vazquez et al. 2009). Any environmental driver that sufficiently increases encounter probability (see Section 2.2) for all species could reduce the neutral barrier to inter- actions and allow species to consistently select their interaction partner with optimally matched traits. This enhanced expression of species preferences would result in reduced spatial or temporal variability because the same interactions would consistently be realized (i.e., network homogeniza- tion; Laliberte ́ & Tylianakis 2010). Reduction of the neutral component of interactions could also lead to exaggeration of patterns of trait matching and phylogenetic congruence (Carnicer et al. 2009) (see Section 2.3). Alternatively, a driver that increases the abundance of a subset of species could result in their overrepresentation in interactions by allowing the neutral component of inter- actions to be overexpressed relative to the trait-based component (Carnicer et al. 2009). Because individual species may differ in the extent to which they engage in neutral interactions, changes to the relative abundance of species can alter network architecture. For example, exotic birds can be less selective in the fruit species on which they feed (i.e., feeding more neutrally on species in proportion to their abundance), and this low selectivity can allow them to fill the gap left by rare or extinct native birds and maintain high network nestedness and connectance (Garcıa et al. 2014).

**Peralta 2015:** Plantation forests (as opposed to native) habitat may impose stresses on parasitoids that constrain them to attack only host species for which they are best adapted. -> Consistent with more stress less generalism.

Native herbivore–parasitoid combinations whose interac- tions contributed the most to the pattern of phylogenetic congruence were more abundant in plantations than in native forests. This stronger co-evolutionary signal in plantation forests suggests that parasitoids in disturbed habitats may only be able to utilize hosts that they have best evolved to attack. Analogously, climate warming has been shown to reduce the niche breadth plasticity of par- asitoids (Lavandero & Tylianakis 2013), suggesting that different environmental changes could reduce the ability of parasitoid communities to suppress a broad range of host species and genotypes in natural systems and biologi- cal control programmes.

@@

Induced by latitude (more generalism in tropics) or diversity (more generalism with high diversity or the opposite), See Baiser 2019 for refsuse network as a random effect.
